MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
Added Accuracy by seconds left on Shot clock

  # dealing with missing values
df[, "SHOT_CLOCK_NONA"] <- df[, "SHOT_CLOCK"]
is.na(df$SHOT_CLOCK_NONA) <- 99

acc_sec24 <- as.numeric
acc_sec24 <- sum(df$SHOT_CLOCK > 23 & df$FGM == 1) / sum(df$SHOT_CLOCK > 23)

>>>>

  # dealing with missing values
df[is.na(df)] <- 99

acc <- data.frame()
acc[, "SECONDS_LEFT"] <- c(1:23)

#accuracy for every second
for (i in 1:23){
  acc[i, "Accuracy"] <- (sum(df$SHOT_CLOCK > i & df$SHOT_CLOCK <= i+1 & df$SHOT_CLOCK != 99 & df$FGM == 1)/ sum(df$SHOT_CLOCK > i & df$SHOT_CLOCK <= i+1 & df$SHOT_CLOCK != 99))}

ggplot(acc, aes(x = SECONDS_LEFT, y = Accuracy)) + geom_point() + geom_smooth()
